---
title: "Discovering Associations Between Products"
author: "Carmen Corvalan, Arnau Simo, Gerardo Parrello"
date: "January 6, 2019"
output: html_document
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
params:
  plot_height: 549
  plot_width: 888
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  cache = FALSE
  )
source("./code.R")
```

## Background
Blackwell Electronics is considering on acquiring Electronidex, a start-up electronics online retailer. Blackwell board of directors would like the Data Analytics team to give a better insight on Electronidex clientele and if it would be a good partnership to consider.  

## Executive Summary
### What is this report about?
Our purpose is to **determine whether the acquisition of Electronidex is convenient for Blackwell Electronics**. To do so, we want to understand the overlapping or lack thereof of customer and products bases for both companies.

Furthermore, we want to understand the possible associations between products based on the analysis of past purchase baskets of Electronidex, in order to uncover possible sinergies between the two companies.

### Conclusions
<!-- We know that Blackwell is like MediaMarket and Electronidex is like a store in carrer Sepulveda. They cater to different people as it seems, the former to general consumers while the latter goes for electronics enthusiasts.-->

First and foremost, we understand that Blackwell Electronics is considering boosting its online market, since its online store is only one year old, and most of Blackwell’s revenues are generated by online sales than by in-store sales. For that matter, the acquisition of Electronidex could be a valuable asset, given all its sales are made through that channel and it could add a lot of experience to the company.

Regarding customers, we can assert that Electronidex has two identifiable customer segments: retail and business. For retail customers, two subgroups, "Apple Enthusiasts" (or Fanboys) and Gamers, stand out from regular retail clients. Distribution for the transactions analyzed is as follows:
```{r}
pie
```

Not only that, we understand that Electronidex catters to a more specific type of client, that at least knows its way around computers, given the current product rooster. Of course, specificity entails quality, which in turn entails higher prices. This, we believe, is a good addition to the Blackwell's strategy, which follows a more generalistic approach, cattering to "all publics".

On current products, we can see the best seller for Electronidex is the iMac, which we believe would be a good candidate to add to Blackwell's inventory.  

```{r}
itemFrequencyPlot(trList[["all"]], topN=10, type="absolute", main = "Top 10 products")
```

Regarding product associations, we have found in the business segment that the Viewsonic Monitor entails with high probability the following purchase of either a HP Laptop or an iMac. We recommend to include these items in the current product inventory.

We have not found relevant associations regarding de retail segment. Nonetheless, for Fanboys, we have found an unusual association that shows the purchase of a Macbook Air following the purchase of an iPhone Charging Cord. We believe this is an example of correlation not meaning causality.

<!--### Acquisition

We do recommend the acquisition of Electronidex by Blackwell Electronics. This is so because -->